---
title: "haztw_vignette"
author: Yi-Chieh Lee
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{haztw_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_knit$set(
  collapse = TRUE,
  root.dir = '/Users/chieh/Desktop/Sinotech_08/TW_all'
)
```

```{r setup}
library(HAZ.TW)
```

## read_fault  
Read the fault file and return a list.   
In this function, you should set up two parameters, `path` and `faultfile`. `Path` is the file where including all of the additional file, such as regional source earthquake location. `Faultfile` is the file name of fault information with FORTRAN formats.

```{r read_fault}
#read_f <- read_fault('data source/AllSource_NTW_WM#6_0531.dat')
# return a list of 64 faults.
```

## fort2table  
This function can let the FORTRAN file transform to the table formats in R. Just put the `faultfile` name in the function.

```{r fort2table}
#f2t <- fort2table('data source/AllSource_NTW_WM#6_0531.dat')
# return a table 
```


## table2fort 
This function can let the table formats in R transform to the FORTRAN file. You should set up three parameters, `icoor`, `inputfile` and `outputname`. `icoor` is the unit of source coordinate (0 is km, 1 is latitude and longitude), `inputfile` is the result of **fort2table** and `outputname` is the name of output file. The output file will save to the root path.

```{r table2fort}
# set icoor == 1
#t2f <- table2fort(1, f2t, 'f2t.txt')
# output the table to .txt file
#
## 1
## 64
## @@Areal_Shallow and_Beneath_Interface_Crustal_Zone
## 1.0		Prob Activity
## 3		nseg model
## 0.20 0.60 0.20		wts for nseg models
## 79		total nb of sources
## ...
```


## plot_all
This function can plot all fault and segment on the map. Just put the result of **read_fault** in the function. In this figure, you can click each segment and get it's name.

```{r plot_all}
#plotall <- plot_all(read_f)
# return a leaflet map
#plotall
```


## plot_segment  
This function can plot the specific fault or segment on the map. Just put the `faultfile` name and the `ID` of fault in the function. By the function **read_fault** or **fort2table**, you can get the ID of fault. In this figure, you can click each segment and get it's name.
```{r plot_segment}
#plotseg <- plot_segment(read_f, 7:10)
# return a leaflet map
#plotseg
```


## figinfo 
If you have some shapefile, you can use this function to get the attribute table of the shapefile.  
In this function, you should set up two parameters, `tabfile` and `newname`, the former means the name of the shapefile and the latter is the file name of the attribute table.

```{r fig_information}
#finfo <- figinfo('SSHAC_Fault.TAB', 'figinfo.txt')
# output the table to .txt file
#
##   ID          Name Length_km FaultType Segment SourceType npts
## 1  1 Ryukyu trench         0        RV      R1  Interface    9
## 2  1 Ryukyu trench         0        RV      R2  Interface    8
## 3  1 Ryukyu trench         0        RV      R3  Interface    7
## 4  2 Manila Trench         0        RV      D1  Interface    5
## 5  2 Manila Trench         0        RV      D2  Interface    8
## 6  2 Manila Trench         0        RV      D3  Interface    6
```


