---
title: "haztw_vignette"
author: Yi-Chieh Lee
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{haztw_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
# knitr::opts_chunk$set(
#   collapse = TRUE,
#   comment = "#>"
# )
knitr::opts_knit$set(
  collapse = TRUE,
  root.dir = '/Users/chieh/Desktop/Sinotech_08/TW_all/data source'
)
```

```{r setup}
library(magrittr)
library(formattable)
library(HAZ.TW)
path <- '/Users/chieh/Desktop/Sinotech_08/TW_all/data source'
faultfile <- 'AllSource_NTW_WM#6_0531.dat'
```

## read_fault  
Read the fault file and return a list.   
In this function, you should set up two parameters, `path` and `faultfile`. `Path` is the file where including all of the additional file, such as regional source earthquake location. `Faultfile` is the file name of fault information with FORTRAN formats.

```{r read_fault}
read_f <- read_fault(path, faultfile)
# return a list of 64 faults.
```

## fort2table  
This function can let the FORTRAN file transform to the table formats in R. Just put the `faultfile` name in the function.

```{r fort2table}
setwd(path)
f2t <- fort2table(faultfile)
# return a table 
#kable(f2t) %>% kable_styling() %>% scroll_box(height = '800px')
```


## table2fort 
This function can let the table formats in R transform to the FORTRAN file. You should set up three parameters, `icoor`, `inputfile` and `outputname`. `icoor` is the unit of source coordinate (0 is km, 1 is latitude and longitude), `inputfile` is the result of **fort2table** and `outputname` is the name of output file. The output file will save to the root path.

```{r table2fort}
# set icoor == 1
t2f <- table2fort(1, f2t, 'f2t.txt')
# output the table to .txt file
head(t2f)
```


## plot_all
This function can plot all fault and segment on the map. Just put the result of **read_fault** in the function. In this figure, you can click each segment and get it's name.

```{r plot_all}
plotall <- plot_all(read_f)
# return a leaflet map
plotall
```


## plot_segment  
This function can plot the specific fault or segment on the map. Just put the `faultfile` name and the `ID` of fault in the function. By the function **read_fault** or **fort2table**, you can get the ID of fault. In this figure, you can click each segment and get it's name.
```{r plot_segment}
plotseg <- plot_segment(read_f, 7:10)
#return a leaflet map
plotseg
```


## fig_information 
If you have some shapefile, you can use this function to get the attribute table of the shapefile.  
In this function, you should set up two parameters, `tabfile` and `newname`, the former means the name of the shapefile and the latter is the file name of the attribute table.

```{r fig_information}
setwd(path)
figinfo <- fig_information('SSHAC_Fault.TAB', 'figinfo.txt')
#formattable(figinfo)
            #align = c("l",rep("r", NCOL(figinfo))))
#kable(figinfo) %>% kable_styling() %>% scroll_box(height = '800px')
```


