---
title: "haztw_vignette"
author: Yi-Chieh Lee
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{haztw_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_knit$set(
  collapse = TRUE,
  root.dir = '/Users/chieh/Desktop/Sinotech_08/TW_all'
)
```

```{r setup}
library(HAZ.TW)
library(leaflet)
library(magrittr)
```

## examine_haz_src  
Before read the fault.src, we should check the note in the fault.src file is correct or not to avoid the warning or error message.  
In this function, you should set up two parameters, `fault.src` and `fault_output`, the former one is the original file name of fault.src and the second one is the new name of fault.src.

```{r examine_haz_src}
examine_haz_src(fault.src = 'data source/TW_all_cgs_14BT.txt',
                fault_output = 'data source/new_cgs_14BT.txt')
```


## read_haz_src

After the step of examine data. We can use **read_haz_src** to read the fault file. This function can let the FORTRAN file transform to the table formats in R. Just put the `fault.src` name in the function.

```{r read_haz_src}
read_f <- read_haz_src(fault.src = 'data source/new_cgs_14BT.txt')
# return a table 
```

## plot_haz_src(unfinish)
After read the fault.src, we can use this function to plot tha map about **read_haz_src**. In this function, ypu should set up two parameters, `faults` and `ID`, the former one is the result of **read_haz_src** and the second one is the ID number of fault. You can get the ID number in the result table of **read_haz_src**(faultID).

```{r plot_haz_src}
#plot_haz_src(faults, ID)
```


## write_haz_src  
This function can let the table formats in R transform to the FORTRAN file. You should set up three parameters, `icoor`, `faults` and `fault_out.src`. `icoor` is the unit of source coordinate (0 is km, 1 is latitude and longitude) and default is 1, `faults` is the result of **read_haz_src** and `fault_out.src` is the name of output file. The output file will save to the root path.

```{r write_haz_src}
write_f <- write_haz_src(icoor =  1, faults = read_f, fault_out.src = 'read_f.txt')

# output the table to .txt file
#
## 1
## 64
## @@Areal_Shallow and_Beneath_Interface_Crustal_Zone
## 1.0		Prob Activity
## 3		nseg model
## 0.20 0.60 0.20		wts for nseg models
## 79		total nb of sources
## ...
```


## read_haz_gis
You can use this function to read the shapefile or any format in GIS. Just set the file name of figure as parameter and it will return an attribute table of `fault_tab`.

```{r read_haz_gis}
read_g <- read_haz_gis(fault_tab = 'data source/SSHAC_Fault.TAB')
```

## plot_haz_gis
This function can help you to demonstrate the figure of `fault_tab`. Just set the result name of **read_haz_gis** as parameter and it will return a map with some information about faults and segments to you.  
```{r plot_haz_gis}
plot_haz_gis(fault_gis = read_g)
```

## write_haz_gis
After finish the GIS data, it's time to write this 
```{r write_haz_gis}
# write_haz_gis(fault_gis = read_g,
#               fault_gis_out = 'read_g_gis',
#               driver = "MapInfo File")
```

